Bird beak's elaboration and innovation

### 2022-02-22 Analysis/09-Figure3.Rmd
Update 09-Figure3.Rmd

pdf("../Manuscript/Figures/Figure3_cd.pdf", height = 12, width = 8)
## Great the plot layout
layout_matrix <- cbind(matrix(0,2,2), matrix(0,2,2))
layout_matrix <- rbind(rbind(layout_matrix, matrix(1:8, 2, 4)), matrix(9:16, 2, 4))
plot_layout <- layout(layout_matrix)
# layout.show(plot_layout)

one.plot.correlations <- function(cor.results, col.sub, col.fun = colour.palette, legend.pos = "topleft", pt.cex = 0.5, legend.cex = 0.5, ID, ...) {

    dots <- list(...)

@@

    # if(!missing(tree)) {
    #     op <- par(mfrow = c(1,2))
    #     #c(bottom, left, top, right); c(5, 4, 4, 2) + 0.1
    #     par(mar = c(5, 4, 4, 0)+0.1)   
    # }

    ## Plotting the results

    ## Selecting the x and y axis base on plot ID
    select.x <- function(ID, yes = "", no = "") {
        # ifelse(ID %in% c(5:8), yes, no)
        return(no)
    }
    select.y <- function(ID, yes = "", no = "") {
        # ifelse(ID == 1 || ID == 5, yes, no)
        return(no)
    }

    par(mar = c(select.x(ID, 4, 2), select.y(ID, 4, 2), 3, 1)+0.1)
    plot(cor.results$x, cor.results$y, pch = 19,
        xlab = select.x(ID, "elaboration"),
        ylab = select.y(ID, "explortation"),
        main = strsplit(cor.results$main, split = ":")[[1]][1],
        cex = pt.cex, col = col_vector,
        ...)

    if(!is.null(col.sub)) {
        legend_text <- levels(col_sub)
        if(length(empty <- which(legend_text == "")) > 0) {
            legend_text[empty] <- "other"
        }
        ## Adding the legend
        legend(x = legend.pos, legend = legend_text, pch = 19, cex = legend.cex, col = col_avail, bg = "white")
    }

@@

## Set the vector of legend positions
legends_pos <- c("topleft", "topright", "topright", "topright", "topleft", "topright", "topleft", "topright", "topright")

for(i in 1:8) {
    one.plot.correlations(super_phylo_cor[[i]],col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.8, legend.cex = 0.8)
}

@@

## Set the vector of legend positions
legends_pos <- c("bottomright", "topright", "topright", "topleft", "topleft", "topright", "bottomright", "bottomright")

for(i in 1:8) {
    one.plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.8, legend.cex = 0.8)
}
dev.off()
```

>>>>

pdf("../Manuscript/Figures/Figure3_cd.pdf", height = 12, width = 8)
## Great the plot layout
layout_matrix <- cbind(matrix(0,2,2), matrix(0,2,2))
layout_matrix <- rbind(rbind(layout_matrix, matrix(1:8, 2, 4, byrow = TRUE)), matrix(9:16, 2, 4,  byrow = TRUE))
plot_layout <- layout(layout_matrix)
# layout.show(plot_layout)

one.plot.correlations <- function(cor.results, col.sub, col.fun = colour.palette, legend.pos = "topleft", pt.cex = 0.5, legend.cex = 0.5, ID, legend_counter) {

@@

    ## Sort the data by group size
    all_data <- cbind(x = cor.results$x, y = cor.results$y)
    ## Classify the groups per numbers of species
    all_data <- data.frame(all_data, col = col_vector)

    ## Sort the data per group size
    group_order <- sort(table(all_data$col), decreasing = TRUE)

    ## Set the plotting data
    plot_data <- data.frame()
    # col_adjust <- seq(from = 1/length(group_order), to = 1, by = 0.1)*3
    for(i in 1:length(group_order)) {
        ## Get the data from the biggest group
        selected_data <- all_data[which(all_data$col == names(group_order[i])), ]
        ## Transparantise the colours (for the background)
        # selected_data$col <- adjustcolor(selected_data$col, alpha = col_adjust[i])
        ## Combine the plotting data
        plot_data <- rbind(plot_data, selected_data)
    }

    ## Plot the points
    plot(plot_data$x, plot_data$y, pch = 19, cex = pt.cex, col = plot_data$col, xaxt = "n", yaxt = "n", xlab = "", ylab = "", main = strsplit(cor.results$main, split = ":")[[1]][1])
    axis(1, at = pretty(plot_data$x, n = 4))
    axis(2, at = pretty(plot_data$y, n = 4), las = 2)

    if(!is.null(col.sub)) {
        ## See if there is any others
        levels <- levels(col_sub)
        if(length(other <- which(levels == "")) > 0) {
            legend_text <- c(1, 1:(length(levels(col_sub))-1)+legend_counter)
        } else {
            legend_text <- c(1:(length(levels(col_sub)))+legend_counter)
        }
        ## Update the legend counter
        legend_counter <<- max(legend_text)
        ## Adding the legend
        legend(x = legend.pos, legend = legend_text, pch = 19, cex = legend.cex, col = col_avail, bg = "white")
    }

@@

## Set the vector of legend positions
legends_pos <- c("topleft", "topright", "topright", "topright",
                 "topleft", "topright", "topleft", "topright")
legend_counter <- 1

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_phylo_cor[[i]],col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter)
}

@@

## Set the vector of legend positions
legends_pos <- c("bottomright", "topright", "topleft", "topleft",
                 "topleft", "topleft", "topright", "bottomright")
legend_counter <- 1

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter)
}
dev.off()
```
